### 2024-05-14 acronyms/acronyms.tex
more acronyms
aec
acronyms
acro
erda
HEAD
R&D
nts
acronym
nwt
irg

@@

>>>>

\newacronym{ym}{YM}{Yucca Mountain}
\newacronym{nwf}{NWF}{Nuclear Waste Fund}
\newacronym{aea}{AEA}{Atomic Energy Act}
\newacronym{aec}{AEC}{Atomic Energy Commission}
\newacronym{un}{UN}{United Nations}
\newacronym{des}{DES}{Discrete Event Simulation}
\newacronym{nem}{NEIM}{Nuclear Engineering \& Industrial Management}
\newacronym{erd}{ERDA}{Energy Research and Development Administration}
\newacronym{rd}{R\&D}{Research \& Development}
\newacronym{nts}{NTS}{Nevada Test Site}
\newacronym{nrm}{NRMSAC}{Nevada Radioactive Materials Storage Advisory Committee}
\newacronym{tmi}{TMI}{Three Mile Island}
\newacronym{nwt}{NWTS}{National Waste Terminal Storage}
\newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}

@@

%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file
